On Sample Size Needed for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2024-01-08 Manuscript/manuscript.tex
Responded to last comment

One of the goals of this study was to provide some practical recommendations for 
necessary sample sizes when using block bootstrap to estimate parameters of 
serially dependent data. When using Student's $t$ intervals and $\phi$ is 
unknown, the results of this study suggest that an $n \geq 800$ may be necessary 
for common practice to estimate simpler parameters like $\mu$ or $\sigma_x$. If 
$\phi$ is already known, a lesser $n$ may be adequate to estimate these 
parameters. For lower absolute values of $\phi$, a smaller $n$ is sufficient 
when estimating $\sigma_x$. For negative values of $\phi$, coverage of all 
parameters is higher in general. In fact, Student's $t$ seems to over-cover 
$\mu$ for $\phi = - 0.4$ when using smaller sample sizes, meaning that if $\phi$ 
is known to have a very negative value, another CI may be required. However, in 
real world applications, $\phi$ is more commonly found to be positive, so 
Student's $t$ should still be used if $\phi$ is unknown. Lastly, to estimate 
$\phi$, $n \geq 100$ using the Student's $t$ method may be sufficient. Further
investigation may be necessary to see if there are other interval corrections
that fix the coverage deterioration problem for $\phi$.

@@

Based on \textbf{Figure~\ref{fig:mu2}}, for negative autocorrelations, the 
coverage 
rates of $\mu$ appear to be lower when
using $l = \lceil 2n^{1/3} \rceil$. For example, whereas $n = 100$ or 200 
would seem sufficient for most CIs when using $l = \lceil n^{1/3} \rceil$, 
$n = 800$ or 1600 is necessary to capture negative autocorrelations for 
$l = \lceil n^{1/3} \rceil$. Student's $t$ CIs do not seem to be as affected
by this change in $l$: for $\phi = -0.4$ and -0.2, they still overcover $\mu$
for smaller values of $n$.

>>>>

One of the goals of this study was to provide some practical recommendations for 
necessary sample sizes when using block bootstrap to estimate parameters of 
serially dependent data. When using Student's $t$ intervals and $\phi$ is 
unknown, the results of this study suggest that an $n \geq 800$ may be necessary 
for common practice to estimate simpler parameters like $\mu$ or $\sigma_x$. If 
$\phi$ is already known, a lesser $n$ may be adequate to estimate these 
parameters. For lower absolute values of $\phi$, a smaller $n$ is sufficient 
when estimating $\sigma_x$. For negative values of $\phi$, coverage of all 
parameters is higher in general. In fact, Student's $t$ seems to over-cover 
$\mu$ for $\phi = - 0.4$ when using smaller sample sizes, meaning that if $\phi$ 
is known to have a very negative value, another CI may be required. However, in 
real world applications, $\phi$ is more commonly found to be positive, so 
Student's $t$ should still be used if $\phi$ is unknown. Lastly, to estimate 
$\phi$, $n \geq 100$ using the Student's $t$ method may be sufficient. Although
we have only used serial dependences as strong as 0.4, we have established the 
trend. When estimating $\mu$, we expect coverage rates to decrease as
$\phi$ approaches 1 - as $\phi$ approaches -1, we may observe increased 
over-coverage. When estimating $\sigma$, we expect a larger sample size to
be necessary as $|\phi|$ gets closer to 1. Lastly, when estimating $\phi$ for
a marginal normal distribution, we 
expect a larger sample size to be necessary as $|\phi|$ approaches 0. However, 
for a marginal exponential distribution, we expect coverage rates of $\phi$ to 
respond
to stronger dependences similarly to coverage rates of $\mu$. Further
investigation may be necessary to see if there are other percentile-based 
interval corrections
that fix the coverage deterioration problem for $\phi$.

@@

Based on \textbf{Figure~\ref{fig:mu2}}, for negative autocorrelations, the 
coverage 
rates of $\mu$ appear to be lower when
using $l = \lceil 2n^{1/3} \rceil$. For example, whereas $n = 100$ or 200 
would seem sufficient for most CIs when using $l = \lceil n^{1/3} \rceil$, 
$n = 800$ or 1600 is necessary to capture negative autocorrelations for 
$l = \lceil n^{1/3} \rceil$. Student's $t$ CIs do not seem to be as affected
by this change in $l$: for $\phi = -0.4$ and -0.2, they still over-cover $\mu$
for smaller values of $n$.
